Classless Java

### 2015-09-25 paper/sections/Formalization.tex
More formalization.

\subsubsection{Auxiliary function: \textsf{mtype}}
- \textsf{mtype(m, C)} : the signature of method m in C.

@@

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\
  m \notin M}
{ \textsf{mtype(m,T)} = \bigcup \textsf{mtype}(m,\overline{D}) } \]

@@

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\
  m \notin M}
{ \textsf{mbody(m,T)} } \]

>>>>

\begin{comment}
\subsubsection{Auxiliary function: \textsf{mtype}}
- \textsf{mtype(m, C)} : the signature of method m in C.

@@

\[ \inferrule{
  IT(T) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\
  m \notin M}
{ \textsf{mtype(m,T)} = \bigcup \textsf{mtype}(m,\overline{D}) } \]
\end{comment}

@@

$\textsf{mbody}(m,C)$ denotes the actual body of method $m$ that interface $C$ owns. It can either be defined originally in $C$ or in its supertypes, and then passed to $C$ via inheritance.

The body of a method $m$ contains the relevant information with respect to that method, like the type of $m$ as well as the modifier. Below shows how the functions $mtype$ and $mmodifier$ are derived from $mbody$.

\[ \textsf{mbody}(m,C) = \textit{modifier } E \spc m(\overline{D} \spc \overline{x}) \{ \text{return } e; \} \] \[ \Rightarrow \textsf{mtype}(m,C) = \overline{D} \to E,\ \textsf{mmodifier}(m,C) = \textit{modifier}\]

\[ \inferrule{
  IT(C) = \text{\emph{ann} interface } C \{ \overline{M} \} \\
  m \notin M}
{ \textsf{mbody}(m,C) = \emptyset } \]

\[ \inferrule{
  IT(C) = \text{\emph{ann} interface } C \{ \overline{M} \} \\
  m \in M}
{ \textsf{mbody}(m,C) = m } \]

\[ \inferrule{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\
  m \notin M
  }
{ \textsf{mbody}(m,C_0) = \textsf{fold}_\textsf{shadow}\cdot\textsf{map}_{\textsf{mbody,}m}\cdot\textsf{subset}(\overline{C}) } \]

\[ \inferrule{
  IT(C_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{
  \overline{M} \} \\
  m \in M
  }
{ \textsf{mbody}(m,C_0) = \textsf{replace}(m, \textsf{fold}_\textsf{shadow}\cdot\textsf{map}_{\textsf{mbody,}m}\cdot\textsf{subset}(\overline{C})) } \]

\subsubsection{Auxiliary function: \textsf{subset}}

\[ \textsf{subset}(\overline{C})=\{\ x\in\overline{C}\ |\ \nexists y\in\overline{C},\ y <: x\ \} \]
